GSE74548: Gene Methylation Enrichment Analysis

### 2022-05-11 gmea.Rmd
small fixes

dm <- read.table("dma3a.tsv")

@@

>>>>

dm <- read.table("dma3a.tsv.gz")

@@

if ( ! file.exists("ReactomePathways.gmt") ) {
  download.file("https://reactome.org/download/current/ReactomePathways.gmt.zip",
    destfile="ReactomePathways.gmt.zip")
  unzip("ReactomePathways.gmt.zip")
}
file.info("ReactomePathways.gmt")
genesets <- gmt_import("ReactomePathways.gmt")
length(genesets)
